Poseidon Adventure

### 2019-06-06 SardinesOnlyatlantisom2SStest.Rmd
align survey and fishery start, note errors

#Years to survey, assuming survey is once per year
survey_years <- survey_sample_full[burnin:(burnin+nyears-1)]

@@

# below fails for fishery data if I keep timestep aligned with year 31
# Error in `[.data.frame`(comp_matrix[[i]], , as.character(bins[[i]])) : undefined columns selected

# assigning fishery comps to year 30 start (remove +1 after floors above) 
# I get a different error
# Error in `[<-.data.frame`(`*tmp*`, indices, "Seas", value = c(1, 1, 1, : replacement has 49 rows, data has 2045

>>>>

#Years to survey, assuming survey is once per year
survey_years <- survey_sample_full[(burnin+1):(burnin+nyears)]

@@

# below fails with two errors (only gets to first when running)

# Error in `[<-.data.frame`(`*tmp*`, indices, "Seas", value = c(1, 1, 1, : replacement has 49 rows, data has 2045

# Error in `[.data.frame`(comp_matrix[[i]], , as.character(bins[[i]])) : undefined columns selected

# both these errors come from the fishery age and length comps when I step
# through the function, survey caal and lengths read in fine

### 2019-06-06 docs/index.Rmd
align survey and fishery start, note errors

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Start on Sardines in the CalCurrent, all true and SS data, May 31, 2019, updated June 5</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Sardines in the CalCurrent run with F and rec dev scenario, all true and SS data, May 31, 2019, updated June 6</a>
